% apple_cinnamon_cookies.tex
% recipe file for homemade apple cinnamon cookies

\begin{recipe}
[%
% ~~ RECIPE OVERVIEW: ~~
	preparationtime = {\unit[1]{h}},
	bakingtime = {\unit[10 - 15]{min}},
	%portion = {\portion{5 - 8}},
	source = {Ana},
	vegetarian = {yes},
	vegan = {no}
]
%
% ~~ RECIPE NAME: ~~
{Apple Cinnamon Cookies}


% ~~ PICTURES ~~
% Appear on top of the page (optional)
% Insert path\to\filename
\graph
{ 
    small=apple_cinamon_cookies,     % small picture
    big=apple_cinamon_cookies2  % big picture
}


% ~~ INTRODUCTION ~~
% History/anecdote on the recipe (optional)
\introduction
{ 
These delicious apple-cinnamon cookies are soft on the inside but crunchy on the outside. You can easily adapt this recipe to your preferred cookie type, Just replace the apple and cinnamon by whatever you'd like!
}


% ~~ INGREDIENTS ~~
% List as '& quantity & item &\\'
% Caution: no return ('\\') after last item!
% [v1.1] Multi-columns: '& quantity1 & item1 && quantity2 & item2 ... &\\'
\ingredients[2] % [v1.1] number of ingredient columns 
{%
    \unit[2]{cups} & flour\\
    \unit[1/2]{tsp} & baking soda\\
    \unit[3/4]{cups} & butter (softened)\\
    \unit[1]{cup} & brown sugar\\
    \unit[1/2]{tsp} & salt\\
    \unit[1/2]{cup} & granulated sugar\\
    \unit[1]{tsp} & vanilla extract\\
    1 & egg\\
    1 & egg yolk\\
    \unit[1/2]{tsp} & cinnamon\\
    1 & apple\\
}


% ~~ PREPARATION ~~
% Steps as '\step{whatever the step is}'
% [until v1.1] Caution: for optimal floating, steps need to be at >= 2
% 				lines long! -> if one-liner, add a return ('\\') 
\preparation{%
    \step{Mix flour, baking soda, cinnamon and salt.}
    \step{On a separate bowl, mix teh butter and the sugar. Add the egg, the egg yolk and the vanilla extract.}
    \step{Mix the content of the two bowls.}
    \step{Take it to the fridge for at least \unit[20]{minutes}.}
    \step{Peel the apple and cut it into tiny cubes and add to the mix.}
    \step{Use an ice-scream scoop to measure the cookie batter and lay scoops on a baking tray about \unit[8]{cm} apart.}
    \step{Bake for about 13 mins at 165ºC (a bit more if your oven doesn't have a fan).}
    \step{Once you take the tray out of the oven, cover it with a clean kitchen cloth (preferably not touching the cookies) and let them cool down for at least \unit[10]{minutes} before taking the cookies out of tray. (When they come out, they are too gooey to be removed from the tray, which is why you need to wait }
} 


% ~~ HINT ~~
% Specific hint (optional)
\hint
{
Make sure not to skip the last step of the recipe!
When the cookies come out, they are too gooey to be removed from the tray, which is why you need to wait for the bottom to harden before removing them.
}

\end{recipe}

% end of recipe file