% vegan_peanut_cookies.tex
% recipe file for homemade apple cinnamon cookies

\begin{recipe}
[%
% ~~ RECIPE OVERVIEW: ~~
	preparationtime = {\unit[40]{mins}},
	bakingtime = {\unit[12 - 14]{min}},
	%portion = {\portion{5 - 8}},
	source = {Ana},
	vegetarian = {yes},
	vegan = {yes}
]
%
% ~~ RECIPE NAME: ~~
{Vegan Peanut Butter Cookies}


% ~~ PICTURES ~~
% Appear on top of the page (optional)
% Insert path\to\filename
\graph
{ 
    %small=pic/glass,     % small picture
    big=Peanut_Butter_Cookies  % big picture
}


% ~~ INTRODUCTION ~~
% History/anecdote on the recipe (optional)
\introduction
{
These banana and peanut butter cookies are not only delicious but also completely vegan! They are soft and moist on the inside.
}


% ~~ INGREDIENTS ~~
% List as '& quantity & item &\\'
% Caution: no return ('\\') after last item!
% [v1.1] Multi-columns: '& quantity1 & item1 && quantity2 & item2 ... &\\'
\ingredients[2] % [v1.1] number of ingredient columns 
{%
    \unit[2]{cups} & flour\\
    \unit[1/2]{tsp} & baking soda\\
    \unit[1/4]{cups} & vegetable butter (softened)\\
    \unit[1/2]{cups} & peanut butter\\
    \unit[1]{cup} & brown sugar\\
    \unit[1/2]{tsp} & salt\\
    \unit[1/2]{cup} & granulated sugar\\
    \unit[1]{tsp} & vanilla extract\\
    2 & crushed ripe bananas\\
    \unit[1/2]{tsp} & cinnamon\\
    \unit[1]{tbsp} & ground linseed in \unit[3]{tbsp} of warm water\\
}


% ~~ PREPARATION ~~
% Steps as '\step{whatever the step is}'
% [until v1.1] Caution: for optimal floating, steps need to be at >= 2
% 				lines long! -> if one-liner, add a return ('\\') 
\preparation{%
    \step{Mix flour, baking soda, cinnamon and salt.}
    \step{On a separate bowl, mix the butter, the peanut butter, the crushed bananas and the sugar. Add the linseed mix and the vanilla extract.}
    \step{Mix the content of the two bowls.}
    \step{Take it to the fridge for at least \unit[20]{minutes}.}
    \step{Use an ice-scream scoop to measure the cookie batter and lay scoops on a baking tray about \unit[8]{cm} apart.}
    \step{Bake for about 13 mins at 165ºC (a bit more if your oven doesn't have a fan).}
    \step{Once you take the tray out of the oven, cover it with a clean kitchen cloth (preferably not touching the cookies) and let them cool down for at least \unit[10]{minutes} before taking the cookies out of tray. (When they come out, they are too gooey to be removed from the tray, which is why you need to wait }
} 


% ~~ HINT ~~
% Specific hint (optional)
\hint
{
Make sure not to skip the last step of the recipe!
When the cookies come out, they are too gooey to be removed from the tray, which is why you need to wait for the bottom to harden before removing them.
}

\end{recipe}

% end of recipe file