% bacalhau a bras.tex
% recipe file for Portuguese Bacalhau à Brás

\begin{recipe}
[%
% ~~ RECIPE OVERVIEW: ~~
	preparationtime = {\unit[15]{min}},
	bakingtime = {\unit[1]{h}},
	portion = {\unit[1]{big pot}},
	source = {Ana},
	country = {Portugal},
	vegetarian = {no},
	vegan = {no}
]
%
% ~~ RECIPE NAME: ~~
{Bacalhau \`{a} Br\'{a}s}


% ~~ PICTURES ~~
% Appear on top of the page (optional)
% Insert path\to\filename
\graph
{ 
    small=bacalhau_bras,     % small picture
    big=bacalhau_bras2  % big picture
}


% ~~ INTRODUCTION ~~
% History/anecdote on the recipe (optional)
\introduction
{ 
One of the most typical Portuguese codfish dishes and my personal favourite: Bacalhau \`{a} Br\'{a}s. It is basically codfish with fries and eggs all mix together beautifully.
}


% ~~ INGREDIENTS ~~
% List as '& quantity & item &\\'
% Caution: no return ('\\') after last item!
% [v1.1] Multi-columns: '& quantity1 & item1 && quantity2 & item2 ... &\\'
\ingredients[2] % [v1.1] number of ingredient columns 
{%
    4 & eggs\\
    1 & onion\\
    6 & big potatoes\\
    3 & garlic cloves\\
    2 & salted codfish fillets\\
    \unit[1/4]{cup} & fresh flat-leaf parsley\\
    \unit[1/2]{tsp} & salt\\
    a lot & olive oil\\
    some & olives (optional)\\
}


% ~~ PREPARATION ~~
% Steps as '\step{whatever the step is}'
% [until v1.1] Caution: for optimal floating, steps need to be at >= 2
% 				lines long! -> if one-liner, add a return ('\\') 
\preparation{%
    \step{Cut the potatoes into thin fries shape, about \unit[3]{cm} long.}
    \step{Fill a frying pan with olive oil about \unit[1]{cm} deep and heat it up the oil is warm (but not too hot).}
    \step{Fry the potatoes until they are just about cooked but don't let them get too soft.}
    \step{Set them aside in some paper towels to soak up the extra grease.}
    \step{Dice the onions and mince the garlic and the parsley.}
    \step{Shred the codfish and mix the eggs.}
    \step{In a big pot, heat up some olive oil and put in the onion and garlic stirring constantly.}
    \step{When the onion have started to get golden, add the shredded codfish and the parsley.}
    \step{Let it cook for a few minutes and then add the egg mix. Stir constantly until the eggs are almost cooked.}
    \step{Add the fries and mix it all, stirring until the eggs are cooked and the potatoes are soft.}
    \step{Serve warm with some olives and enjoy!}
} 


% ~~ HINT ~~
% Specific hint (optional)
\hint
{
If you can't find salted codfish, just get fresh codfish and leave it covered in salt for about 1h. Make sure to rinse all the extra salt before using!
}


\end{recipe}

% end of recipe file