% pataniscas.tex
% recipe file for Portuguese pataniscas

\begin{recipe}
[%
% ~~ RECIPE OVERVIEW: ~~
	preparationtime = {\unit[10]{min}},
	bakingtime = {\unit[30]{min}},
	portion = {\portion{8 - 12}},
	source = {Ana},
	country = {Portugal},
	vegetarian = {no},
	vegan = {no}
]
%
% ~~ RECIPE NAME: ~~
{Pataniscas}


% ~~ PICTURES ~~
% Appear on top of the page (optional)
% Insert path\to\filename
\graph
{ 
    %small=pic/glass,     % small picture
    big=pataniscas  % big picture
}


% ~~ INTRODUCTION ~~
% History/anecdote on the recipe (optional)
\introduction
{ 
A classic Portuguese dish, pataniscas are basically little codfish cakes seasoned with absolute delicioussness. They go especially well with Arroz de feijão (rice and beans) or some other form of rice.
}


% ~~ INGREDIENTS ~~
% List as '& quantity & item &\\'
% Caution: no return ('\\') after last item!
% [v1.1] Multi-columns: '& quantity1 & item1 && quantity2 & item2 ... &\\'
\ingredients[2] % [v1.1] number of ingredient columns 
{%
    6 & eggs\\
    2 & salted codfish fillets\\
    2 & minced garlic cloves\\
    \unit[4]{tbsp} & corn starch\\
    \unit[1/4]{cup} & diced fresh flat-leaf parsley\\
    \unit[1/2]{tsp} & salt\\
    enough & vegetable oil (to deep fry)\\
}


% ~~ PREPARATION ~~
% Steps as '\step{whatever the step is}'
% [until v1.1] Caution: for optimal floating, steps need to be at >= 2
% 				lines long! -> if one-liner, add a return ('\\') 
\preparation{%
    \step{Shred the codfish.}
    \step{Mix all the ingredients (except the oil)}
    \step{Fill a frying pan with oil and heat it up until the oil is hot.}
    \step{Take out bits of the batter with a ladle (about 2/3 full) and fry them until golden.}
    \step{Set them aside in some paper towels to soak up the extra grease.}
    \step{Serve with whatever side you have and enjoy!}
} 


% ~~ SUGGESTIONS ~~
% Chef suggestions (optional)
\suggestion
[Add some frozen shrimp] % suggestion title
{ 
To make them even better, had \unit[2/3]{cup} of frozen peeled shrimp to the batter.
}

% ~~ HINT ~~
% Specific hint (optional)
\hint
{
If you can't find salted codfish, just get fresh codfish and leave it covered in salt for about \unit[1]{h}. Make sure to rinse all the extra salt before using!
}


\end{recipe}

% end of recipe file